### 2017-04-28 sec-intro.tex
Update abstract/intro to focus on the behavior representation.
This also adds another figure that gives a basic example of an
idealized version of what the behavior representation we propose could
capture.

\section{Introduction}
The proliferation of massive open online courses (MOOCs) has resulted in a
profound impact on education. As more and more learners turn to MOOCs to
educate themselves on various topics, more and more behavioral data is
being collected as part of the system on which the MOOC is offered. The
data present in these logs has the power to aid us in understanding the
behavior of students who take our MOOCs, which is mostly undetectable for
instructors of these MOOCs today due to its vast scale. As a result, the
rich data available through these MOOC logs is highly underutilized today.

What stands in the way? Clearly, intelligent systems to create concise and
digestible summaries of the massive amount of interaction data collected
are needed in order to empower the instructors of these courses. If we can
understand how users are interacting with our MOOCs, we are much more
likely to be able to make changes to these courses that positively impact
learners. While we can easily observe the changes in behavior of students
in real classrooms, MOOCs present a challenge due to their hands-off
nature and sometimes irregular schedule due to being a full-time worker.   
We view this paper as attempting to bridge this gap. Specifically,
in this paper we propose unsupervised learning methods for automatically
discovering and characterizing student learning behavior patterns or profiles from large
collections of click logs associated with MOOCs.

We view our model as a component of a system that enables collaboration
between the machine and a human instructor to extract knowledge from these
large collections of MOOC data. Automatically extracting interpretable
patterns from the clickstream data associated with MOOCs is a necessary
step in order for instructors to identify the hidden knowledge in these
massive interaction datasets. Without the availability of a suitable model
for identifying these behavioral patterns, instructors are not empowered to
use this available data to improve their courses without expending
extraordinary amounts of manual effort.

>>>>

\section{Introduction}

The proliferation of massive open online courses (MOOCs) has resulted in a
profound impact on education. As more and more students participate in
these novel educational environments, it is of utmost importance that we be
able to understand the behavioral patterns of students as they interact
with them. While we can easily observe the changes in behavior of students
in real classrooms, MOOCs present a challenge due to their hands-off nature
and sometimes irregular schedule due to being a full-time worker.

At the same time, as more and more learners turn to MOOCs to educate
themselves on various topics, more and more behavioral data is being
collected as part of the system on which the MOOC is offered. This
presents a unique opportunity: the data present in these logs has the power
to aid us in understanding the behavior of students who take our MOOCs,
which is mostly undetectable for instructors of these MOOCs today due to
its vast scale. As a result, the rich data available through these MOOC
logs is highly underutilized today.

What stands in the way? Clearly, intelligent systems to create concise and
digestible summaries of the massive amount of interaction data collected
are needed in order to empower the instructors of these courses. If we can
understand how users are interacting with our MOOCs, we are much more
likely to be able to make changes to these courses that positively impact
learners. We view this paper as attempting to bridge this gap.

How should we represent behavioral patterns, and what does it mean to
understand changes in student behavior with respect to these patterns?
These are still very open questions, and are active areas of
research~\cite{Kizilcec:2013:LAK, Faucon:2016:EDM, Davis:2016:EDM,
Shih:2010:EDM}. In this paper, we advocate for a particular representation
of student behavior patterns as well as \emph{behavior transitions} that we
believe is simultaneously interpretable but also amenable to unsupervised,
automated discovery via statistical means. Specifically, we choose to
visualize behavior patterns as labeled directed graphs where node sizes are
proportional to steady-state probabilities and edge widths are proportional
to the probability of leaving a node following that edge. We can use this
same representation for visualizing both the student behavior patterns as
well as the transitioning behavior between them. In
Figure~\ref{fig:motivating-example} we show a hypothetical example of the
kind of output our proposed representation could convey. Here we see two
different behavioral patterns (\ref{fig:motivating-example-0} and
\ref{fig:motivating-example-1}) as well as the \emph{transition behavior}
between these two behavior patterns (\ref{fig:motivating-example-trans}).
\begin{figure}
  \centering
  \begin{subfigure}[t]{0.30\textwidth}
    \includegraphics[width=\textwidth]{figures/example/state0.png}
    \caption{Behavior pattern 0\label{fig:motivating-example-0}}
  \end{subfigure}
  \begin{subfigure}[t]{0.30\textwidth}
    \includegraphics[width=\textwidth]{figures/example/state1.png}
    \caption{Behavior pattern 1\label{fig:motivating-example-1}}
  \end{subfigure}
  \begin{subfigure}[t]{0.30\textwidth}
    \includegraphics[width=\textwidth]{figures/example/trans.png}
    \caption{Transitions between the two behavior patterns to the
    left.\label{fig:motivating-example-trans}}
  \end{subfigure}
  \caption{An idealized example of what our behavior representation could capture.}
  \label{fig:motivating-example}
\end{figure}
We could infer many things from even such a simple example. The first might
be that, when students are taking quizzes, they tend to either use the
forum or the videos for support, but not both. They also tend to take
quizzes in a sort of ``cycle'' pattern, indicating perhaps that this course
allows quiz re-takes. Finally, in Figure~\ref{fig:motivating-example-trans}
we could conclude that users tend to change their quiz-taking behavior over
time from one that is more video-focused (pattern 0) to one that is more
forum-focused (pattern 1).

Our goal in this paper is to design a model that can automatically capture
student behavior in this way via unsupervised learning methods applied to
large collections of click logs associated with MOOCs. We view our model
as a component of a system that enables collaboration between the machine
and a human instructor to extract knowledge from these large collections of
MOOC data. Automatically extracting interpretable patterns from the
clickstream data associated with MOOCs is a necessary step in order for
instructors to identify the hidden knowledge in these massive interaction
datasets. Without the availability of a suitable model for identifying
these behavioral patterns, instructors are not empowered to use this
available data to improve their courses without expending extraordinary
amounts of manual effort.
